\documentclass[english]{scrartcl}
\usepackage{fontspec}
%\setmainfont{Latin Modern Roman}
\usepackage{lmodern}
\usepackage{babel}
\usepackage{mathtools, amssymb, dsfont, amsthm}
\usepackage[mathcal]{eucal}
\usepackage{tikz-cd}
\usepackage{enumitem}
\newcommand*{\embrace}[1]{(#1)}
\usepackage{scrlayer-scrpage}
\usepackage[backend=biber]{biblatex}
\bibliography{steenrod_algebra.bib}
\usepackage{hyperref}
\hypersetup{%
  pdfauthor=Gesina Schwalbe,
  pdftitle=The Steenrod Algebra and its Modules}

\theoremstyle{definition}
\newtheorem*{Def}{Definition}
\newtheorem*{DefLem}{Definition/Lemma}
\newtheorem*{Thm}{Theorem}
\newtheorem*{Prop}{Proposition}
\newtheorem*{Lem}{Lemma}
\newtheorem*{Rem}{Remark}
\theoremstyle{remark}
\newtheorem*{Ex}{Example}



\newcommand*{\idest}{i.\,e.\ }
\newcommand*{\suchthat}{s.\,t.\ }

\newcommand*{\SP}{\ensuremath{\mathcal{SP}}}
\newcommand*{\N}{\mathds{N}}
\newcommand*{\Z}{\mathds{Z}}
\newcommand*{\Zmod}{\Z/2}
\newcommand*{\R}{\mathds{R}}
\newcommand*{\id}{\text{id}}

\newcommand*{\mult}{\bigtriangledown} % multiplication of algebra
\newcommand*{\comult}{\bigtriangleup} % co-multiplication of co-algebra
\newcommand*{\unit}{\eta} % unit of algebra
\newcommand*{\counit}{\varepsilon} % co-unit of co-algebra
\newcommand*{\multmod}{\mu} % scalar multiplication of module over algebra
\newcommand*{\m}{*} % short for scalar multiplication
\newcommand*{\SteenrodAlg}{\mathcal{A}} % Steenrod algebra
\newcommand*{\one}[1]{1_{#1}} % unit (i.e. image of 1 under unit map)
\newcommand*{\Sq}{\text{Sq}} % Steenrod square
\newcommand*{\ev}{\text{ev}} % evaluation


\begin{document}
\clearpairofpagestyles
\ohead*{05/07/2017, University of Regensburg}
\ihead*{Gesina Schwalbe}
\cfoot*{\pagemark}

\begin{center}
  Seminar on Stable Homotopy Theory – Summary

  \medskip
  {\Large\bfseries The Steenrod Algebra and its Modules}
\end{center}
\smallskip

\begin{Def}
  Let $R$ be a commutative ring with unit.
  \begin{enumerate}[label=(\arabic*), parsep=0pt, listparindent=\parindent]
  \item A \emph{graded $R$-module} is an $R$-module of the form
    $M_*=\bigoplus_{i\in\N} M_i$ with $M_i$ $R$-modules.
    Write $\deg m = i$ iff $m\in M_i$.

    A \emph{graded submodule} of $M_*$ is a graded $R$-module $Q_*$,
    \suchthat $Q_i\subset M_i$
    (\idest $N$ is generated by homogenous elements).

    A \emph{graded $R$-module homomorphism} is an $R$-homomorphism $f\colon
    M_*\to N_*$ of graded $R$-modules with $f(M_i)\subset N_i$
    (\idest $f=f_*$).
    The kernel of $f$ is a graded submodule.

    \begin{Ex}
      $M_*\otimes N_* = \bigoplus_{i\in\N}\bigoplus_{r+s=i}
      M_i\otimes N_i$ is graded $R$-module.
    \end{Ex}
  \item\label{def:algebra}
    A \emph{graded $R$-algebra} $(A,\mult,\unit)$ is a graded
    $R$-module $A_*$ with
    \begin{enumerate}
    \item (\emph{multiplication}) a graded $R$-homomorphism
      $\mult=(-\cdot-)\colon A\otimes A\to A$
    \item (\emph{unit}) a graded $R$-homomorphism
      $\unit\colon R\to A_*$
    \end{enumerate}
    \suchthat
    $A_*\cong A_*\otimes R
    \xrightarrow{\id\otimes\unit} A_*\otimes A_*
    \xrightarrow{\mult} A_*$ is $\id_A$ (and the same for $R\otimes
    A_*$),
    \idest
    $A$ has unit $\one{A}\coloneqq \unit(1_R)$
    with $\one{A}\cdot a=a=a\cdot\one{A}$ for $a\in A$.

    A \emph{(graded) $R$-algebra homomorphism} is a graded $R$-module
    hom.\  ${f\colon A_*\to B_*}$, \suchthat
    $f(a\cdot a') = f(a)\cdot f(a')$ for $a,a'\in A$ and $f(\one{A})=\one{B}$.

    \begin{Ex}
      $(A_*\otimes B_*, \mult_{A\otimes B},\unit_A\otimes\unit_B)$
      is a graded $R$-algebra with multiplication
      \begin{gather*}
      (a_1\otimes b_1)\cdot(a_2\otimes b_2)\coloneqq 
      (-1)^{\deg(b_1)\deg(a_2)} (a_1\cdot a_2)\otimes(b_1\cdot b_2)\;.
    \end{gather*}
  \end{Ex}
  \item\label{def:algebraprop} A graded $R$-algebra $A$ is called ($a,b,c\in A$)
    \begin{description}[font=\normalfont\itshape, noitemsep]
    \item[associative]
      iff $(a\cdot b)\cdot c=a\cdot(b\cdot c)$,
    \item[(graded) commutative]
      iff $a\cdot b=(-1)^{\deg(a)\deg(b)}b\cdot a$,
    \item[augmented]
      iff $\unit$ as a graded retraction $\counit$ (called \emph{co-unit}),
    \item[connected]
      iff $A$ is augmented and $\counit_0\colon A_0\to R$ is an isomorphism.
    \end{description}
    
    \begin{Ex}
      $(H^*(X;R),\cup)$ is a graded, ass., comm., and
      connected $R$-algebra.
    \end{Ex}
  \item A \emph{graded $R$-co-algebra} $(A,\comult,\counit)$ is defined by
    inversing all arrows in \ref{def:algebra} and \ref{def:algebraprop}.
    $\comult$ is called \emph{co-multiplication} or diagonal, and $\counit$
    is called \emph{co-unit}.
  \item A \emph{Hopf algebra} $(A,\mult,\unit,\comult)$ over $R$ is a
    connected, graded $R$-algebra $(A,\mult,\unit)$ with co-unit
    $\counit$ and a graded homomorphism of $R$-algebras
    $\comult\colon A_*\to A_*\otimes A_*$,
    \suchthat $(A,\comult,\counit)$ is an $R$-co-algebra.
  \item A \emph{(left-)module} over a graded $R$-algebra $A_*$ is
    a graded $R$-module $M$ with a scalar multiplication
    $\multmod=(-\m-)\colon A_*\otimes M_*\to M_*$,
    \suchthat for $m\in M$, $g,h\in A$
    \begin{enumerate}
    \item $\one{A}\m m = m$
    \item $(g\cdot h)\m m = g\m(h\m m)$
    \end{enumerate}
  \end{enumerate}
\end{Def}


\begin{DefLem}[Steenrod Algebra]
  Consider the graded $\Zmod$-algebra
  \begin{gather*}
    \tilde \SteenrodAlg
    \coloneqq \bigoplus_{\mathclap{i\in\N}}
      \left\langle \Sq^{\otimes I}
      \;\middle|\;
      I\subset\N\text{ family of length $i$} \right\rangle_{\Zmod}
  \end{gather*}
  with multiplication $\otimes$, and the graded ideal
  (compare first part with the Adem relations!)
  \begin{align*}
    \text{Rel}_*
    \coloneqq
    &\left(
      \Sq^a\otimes \Sq^b
      - \sum_{c=0}^{\lfloor \frac{a}{2} \rfloor}
      {\scriptstyle\binom{b-c-1}{a-2c}} \Sq^{a+b-c}\otimes\Sq^c
      \;\middle|\; 0<a<2b \right)_{\tilde{\SteenrodAlg}}
      + \left( \Sq^0 - \one{\Zmod}\right)_{\tilde{\SteenrodAlg}}     
  \end{align*}
  Then $\SteenrodAlg\coloneqq \tilde{\SteenrodAlg}/ \text{Rel}_*$
  is a graded, associative, connected, non-commutative 
  $\Zmod$-algebra, called the \emph{Steenrod algebra}.
  It has $\Zmod$-basis $\{\Sq^{\otimes I}|I\text{ admissible sequ.}\}$
  and is (not freely) generated as $R$-algebra by the indecomposable
  subset $\{\Sq^{2^i}\,|\,i\in\N\}$.
  \begin{proof}[proof (scetch)]
    Use the (graded) evaluation homomorphism
    $\Sq^{\otimes I}\mapsto \Sq^I(\sigma_n)$ for linear independence;
    the Adem relations together with an induction on the momentum of a
    sequence for the generating system property.
    Note: $\Sq^k$ is decomposable iff $k\neq 2^i$.
  \end{proof}
\end{DefLem}

\begin{DefLem}
  The graded $\Zmod$-algebra homomorphism defined by
  \begin{gather*}
    \tilde{\SteenrodAlg}\to \SteenrodAlg\otimes\SteenrodAlg\;,\quad
    \Sq^i\mapsto\sum_{r+s=i}\Sq^r\otimes\Sq^s
  \end{gather*}
  induces a well-defined co-multiplication on $\SteenrodAlg$ making it
  a Hopf algebra.
\end{DefLem}

\begin{Ex}
  $H^*(X;R)$ together with the evaluation
  \begin{gather*}
    \ev\colon\SteenrodAlg\to H^*(X)\;,\quad
    \Sq^{\otimes I}\otimes x\mapsto \Sq^I(x)
  \end{gather*}
  is a left-module over $\SteenrodAlg$
  (even a left-algebra, \idest $\ev$ is compatible with $\cup$).
\end{Ex}


\begin{Prop}
  Let $(A,\mult, \unit, \comult)$ be a Hopf $K$-algebra, and
  $(M,\comult_M,\counit_M, \multmod=\m)$ a connected $A$-co-algebra with
  co-unit $\one{M}\coloneqq \counit_M^{-1}(\one{K})$.
  If $A\to M,\;a\mapsto a\m \one{M}$ is injective, $M$ is free,
  \idest $M\cong \bigoplus_{i_k\in I} A_{*+i_k}$.
  \begin{proof}[proof (scetch)] \cite[see][Lemma p.\,94]{stong}
    Show that
    $\phi\colon A_*\otimes N_*\to M_*,\;a\otimes n\mapsto a\m s(n)$
    is a (graded) isomorphism, where $N_*\coloneqq M/(A_{>0}\m M)$ and
    $s\colon N\to M$ is any fixed retract of the (vector space) projection.
    For surjectivity make an induction on the degree;
    for injectivity show that the composition
    $((id\otimes\pi)\circ\comult_M) \circ \phi$,
    and hence $\phi$, is (degreewise) injective. Here we use
    injectivity of $a\mapsto a\m 1_M$.
  \end{proof}
\end{Prop}


\nocite{*}
\printbibliography
\end{document}

